Fusing Filters with Integer Linear Programming

### 2014-05-12 2014betterfusionforfilters/section/01-Introduction.tex
benchmark ref

\item
We present benchmarks of our algorithm applied to several common programming patterns, and to several pathological examples.
Our algorithm is complete and yields good results in practice, though if array sizes are unknown, an optimal solution is uncomputable in general. \TODO{ref}
\end{itemize}

>>>>

\item
We present benchmarks of our algorithm applied to several common programming patterns, and to several pathological examples.
Our algorithm is complete and yields good results in practice, though if array sizes are unknown, an optimal solution is uncomputable in general (\S\ref{s:Benchmarks}).
\end{itemize}
